---
output:
  md_document:
    toc: true
    toc_depth: 3
  pdf_document:
    smart: false
  html_document:
    smart: false 
---
# StockPriceSimulator




## Introduction
This package provide a way to simulate a fully random stock ticker based on
theory provided by __"Stochastic Calculus For Finance ii", Shreve"__



## Functions provided by the package
### Key functions

 * Stock price generator for a single instance: [sstock()](sstock)
 * Stock price generator for a single instance, using the Ito's formula approximation
 [sstock\_ito()](sstock\_ito)

## Description of the functions as they was created and defined
### sstock()

#### Summary

It returns a data.frame containing the following variables:

 * time_periods
 * stock_price_path

#### Arguments

| Arguments | Default | Description |
|---|---|---|
| time_to_maturity | 4 | Final time up to the Stock Price Path goes |
| seed | 1 | It fixes initial value of the pseudo random number generation in order to get reproducible experiments. |
| scale | 100 | Define the partition of the time period. |
| sigma | 1 | |



#### Example of Usage

```{r}
library(StockPriceSimulator)
stock_tick <- sstock()
```

```{r echo=FALSE}
ggplot2::ggplot(stock_tick, 
                ggplot2::aes(time_periods, stock_price_path)) +
  ggplot2::geom_point()
```
### sstock\ito()

#### Summary

It returns a data.frame containing the following variables:

 * time_periods
 * stock_price_path
 
The computed path is based on approximation given by the Itô's formula.

#### Arguments

| Arguments | Default | Description |
|---|---|---|
| time_to_maturity | 4 | Final time up to the Stock Price Path goes |
| seed | 1 | It fixes initial value of the pseudo random number generation in order to get reproducible experiments. |
| scale | 100 | Define the partition of the time period. |
| sigma | 1 | standard deviation of the stock |
| alpha | 0 | Mean trend


#### Example of Usage

```{r}
library(StockPriceSimulator)
## Call the path generating function from equation:
stock_tick <- sstock(scale = 1000)
## Call the path generating function from Itôs approximation
stock_tick_ito <- sstock_ito(scale = 1000)
```

```{r echo=FALSE}
ggplot2::ggplot(stock_tick, 
                ggplot2::aes(time_periods, stock_price_path)) +
    ggplot2::geom_point(color = 'pink') +
        ggplot2::geom_line(data = stock_tick_ito,
                           ggplot2::aes(time_periods, stock_price_path),
                           color = 'steelblue')
```
